%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fontawesome}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{David M.}
	    {Perry}
	    {\href{mailto:david.perry880@gmail.com}{david.perry880@gmail.com}}
	    {270.543.9208}
        {\href{https://davidmitchelperry.com}{davidmitchlperry.com}}
	    {\href{www.github.com}{\faGithub \  github.com}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 
	\vspace{-.2in}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Purdue University}
\descript{M.S. in Computer Science}
\location{Spring 2019 \\ West Lafayette, IN}
\sectionsep


\subsection{University of Kentucky}
\descript{B.S. in Computer Science}
\location{Spring 2013 \\ Lexington, KY}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Languages}
C \textbullet{}   C++ \textbullet{} Python \textbullet{} Assembly \\
Java \textbullet{} Ruby \textbullet{} Javscript/Typescript \textbullet{} R \\
\textbullet{} Go \LaTeX \textbullet{} HTML \textbullet{} CSS \textbullet{} MySQL \\
\sectionsep

\subsection{Environments}
Linux \textbullet{} Windows \textbullet{} Android \\ 
OpenBSD
\sectionsep

\subsection{Libraries/Tools}
React \textbullet{} git \textbullet{} NextJS \\
NestJS \textbullet{} React Native \textbullet{} \\ 
Angular \textbullet{} NodeJS \textbullet{} IDA \\
GCloud \textbullet{} Microsoft Azure
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Graduate}

Software Engineering \\
Operating Systems \\
Security \\
Automated Program Reasoning \\
Parallel Computing \\
Networking \\
Compilers \\
Algorithms \\
Modeling and Simulation
\sectionsep

\subsection{Undergraduate}
Software Engineering \\
Operating Systems \\
Security \\
Networks \\
Programming Languages \\
Algorithms \\
Theory of Computing \\
Artificial Intelligence\\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 
	\vspace{-.2in}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Curtain Call LLC}
    \descript{| Founder and Software Engineer }
\location{2022 – Present | Louisville, KY}
\vspace{.05in} % Hacky fix for awkward extra vertical space
    As a full-stack software engineer, I developed and maintained, 
    \href{https://curtaincalltickets.com}{Curtain Call}, a
    SaaS platform for venues to manage their events, ticket sales, and customer
    relationships. The platform is fully hosted in the cloud using multiple
    google services including: Cloud Run, Cloud Build, Cloud Storage, Cloud
    Functions, and Firebase. Over the last year, the platform has sold over
    over 50,000 tickets and processed over \$1,000,000 in ticket sales.
\vspace{.15in} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item {\fontspec[Path = fonts/lato/]{Lato-Bol}\selectfont\bfseries Admin Dashboard:}
created an advanced admin dashboard using Next.js and TailwindCSS. This
    dashboard allows venue operators to efficiently create and manage their
    events, oversee ticket sales, and handle customer support operations
	\vspace{.05in} % Hacky fix for awkward extra vertical space
\item {\fontspec[Path = fonts/lato/]{Lato-Bol}\selectfont\bfseries Customer Website:}
    Developed a customer-oriented website using Next.js and TailwindCSS, which
    features a secure ticket purchasing system through Stripe.
	\vspace{.05in} % Hacky fix for awkward extra vertical space
\item {\fontspec[Path = fonts/lato/]{Lato-Bol}\selectfont\bfseries Backend Server:}
    Implemented a robust server using NestJs to manage all backend
    functionalities, including event coordination, ticket inventory control,
    customer service workflows, and email dispatch for ticket distribution via
    Sendgrid API.
	\vspace{.05in} % Hacky fix for awkward extra vertical space
\item {\fontspec[Path = fonts/lato/]{Lato-Bol}\selectfont\bfseries Javascript Widget:}
    Created a JavaScript widget that can be embedded seamlessly into any
    website. This widget automatically updates with event details and ticket
    availability, facilitating event promotions directly on venue websites.
	\vspace{.05in} % Hacky fix for awkward extra vertical space
\item {\fontspec[Path = fonts/lato/]{Lato-Bol}\selectfont\bfseries Mobile App For Ticket Verification:}
    Developed a mobile application using React Native that enables venue staff
    to scan ticket QR codes using either the device’s built-in camera or an
    external Bluetooth scanner.
	\vspace{.05in} % Hacky fix for awkward extra vertical space
\item {\fontspec[Path = fonts/lato/]{Lato-Bol}\selectfont\bfseries Automated Reporting with Google Cloud Functions:}
    Utilized Google Cloud Functions and Google Cloud Tasks to establish
    automated cron jobs. These jobs periodically send detailed reports to venue
    owners and artist managers.
	\vspace{.05in} % Hacky fix for awkward extra vertical space
\end{tightemize}
\sectionsep

\runsubsection{InfoBeyond LLC}
\descript{| Software Engineer and Operations Manager }
\location{2019 – 2022 | Louisville, KY}
\vspace{.05in} % Hacky fix for awkward extra vertical space

I worked as a software engineer to develop and maintain a Software as a Service
(SaaS), \href{https://www.preworkscreen.com}{Preworkscreen} for companies to
manage their employees's health and safety during the COVID-19 pandemic.
Additionally, I worked on variouis SBIR and STTR research projects awared to
the company by the DoD, DoE, NSF, and NIST.

\vspace{.15in} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item {\fontspec[Path = fonts/lato/]{Lato-Bol}\selectfont\bfseries Preworkscreen}
	\vspace{.05in} % Hacky fix for awkward extra vertical space
	\begin{tightemize}
		\item[$-$] Designed and implemented all of the platform's marketing website using HTML, CSS, and C\# Razor Pages.
        \item[$-$] Implemented customer-specific requirements, including custom questionnaires, reports, and branding, through code modifications and MySQL database updates.
        \item[$-$] Managed SOC II accreditation in a Microsoft Azure environment, enhancing security through strict backup policies, advanced malware analysis, and robust authentication controls. Additionally, I enforced workplace policies covering password management, document control, and employee training to ensure compliance and data protection.
        \item[$-$] Helped grow the platform from 0 to 2,000 paying customers with monthly subscriptions.
	\end{tightemize}

\vspace{.05in} % Hacky fix for awkward extra vertical space
\end{tightemize}
\sectionsep

\end{minipage} 

\newpage


\namesection{David M.}
	    {Perry}
	    {\href{mailto:david.perry880@gmail.com}{david.perry880@gmail.com}}
	    {270.543.9208}
	    {website.com}
	    {\href{www.github.com}{\faGithub \  github.com}}
   
\section{Experience (Continued)}
\sectionsep

\begin{tightemize}
\item {\fontspec[Path = fonts/lato/]{Lato-Bol}\selectfont\bfseries SBIR/STTR Projects}
	\begin{tightemize}
		\vspace{.05in} % Hacky fix for awkward extra vertical space
    \item \href{https://www.securitypolicytool.com}{Security Policy Tool}- Developed a system that allows engineers to create and enforce security policies on their platforms to ensurce compliance with National Institute of Standards and Technology (NIST) federal access control requirements: NIST SP 800-192, 800-162, NISTIR 7316, NISTIR 7874, SP 800-37, and SP 800-53/53A.
    \item \href{https://www.infobeyondtech.com/vehchain/}{VehChain}- Developed an intra-vehicle cybersecurity program for validating communications between trusted and entrusted vehicle control systems. The system secures, authenticates, and responds to threats in a distributed way using blockchain technologies.
    \end{tightemize}
\end{tightemize}
\sectionsep


\runsubsection{Purdue University}
\descript{| Research Assistant }
\location{2014 – 2019 | West Lafayette, IN}
\vspace{.05in} % Hacky fix for awkward extra vertical space
Worked with advisors, \href{https://www.cs.purdue.edu/homes/xyzhang/}{Xiangyu Zhang} and 
\href{https://www.cs.purdue.edu/homes/roopsha/}{Roopsha Samanta}, researching topics in
the field of software engineering, programming languages, and program verification. 
\vspace{.15in} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item {\fontspec[Path = fonts/lato/]{Lato-Bol}\selectfont\bfseries Symbolic Execution Optimizations}
	\vspace{.05in} % Hacky fix for awkward extra vertical space
	\begin{tightemize}
		\item[$-$] Found optimizations that drastically reduce the time required to symbollically execute
		   programs that are control dependent on large arrays
	   	\item[$-$]Implemented optimization in the symbolic execution engine KLEE 
	\end{tightemize}
	\vspace{.05in} % Hacky fix for awkward extra vertical space
\item {\fontspec[Path = fonts/lato/]{Lato-Bol}\selectfont\bfseries Program Clustering}
	\begin{tightemize}
		\vspace{.05in} % Hacky fix for awkward extra vertical space
		\item[$-$] Implemented a tool, SemCluster, that leverages machine learning and
			   program semantics to classify programs based on their bugs and
			   implementation strategies
	\end{tightemize}
\end{tightemize}
\sectionsep

\runsubsection{MIT Lincoln Laboratory}
\descript{| Summer Intern }
\location{Summer 2014, 2015 | Lexington, MA}
\vspace{.05in} % Hacky fix for awkward extra vertical space
Worked with advisor \href{https://www.ll.mit.edu/biographies/hamed-okhravi}{Hamed Okhravi}
in the Cyber Analytics and Decision systems group to
develop a tool, TRACER, for defending against information leaks and memory disclosures.
%Developed a tool, TRACER, that protects Commercial off the Shelf executables without
%source by encrypting their import address table.
\sectionsep

\runsubsection{Purdue University}
\descript{| Teaching Assistant}
\location{2014 – 2018 | West Lafayette, IN}
\begin{tightemize}
	\item Intro. to C Programming (Fall 2018) 
	\item Graduate Software Engineering (Fall 2017)
	\item Software Testing (Spring 2017)
	\item Networking (Spring 2014)
\end{tightemize}
\sectionsep

\runsubsection{Sandia National Laboratory}
\descript{| Cyber Defenders Intern}
\location{Summer 2012 | West Lafayette, IN}
Worked with a team of interns researching malware detection,
genetic programming
algorithms, and super computer simulations.
%\begin{tightemize}
%	\item Extended an intrusion detection system to support malware detection
%%	\item Implemented genetic programming algorithms in Go
%%	\item Developed a program to check the status of individual nodes of a super computer cluster
%\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\section{Publications}

{\fontspec[Path = fonts/lato/]{Lato-Bol}\fontsize{10pt}{12pt}\selectfont\bfseries \underline{Perry, D.} M., Kim, D., Samanta, R., \& Zhang, X. (2019, June). 
SemCluster: Clustering of Imperative Programming
Assignments Based on Quantitative Semantic Features. In Proceedings of the 40th ACM SIGPLAN Conference on Programming
Language Design and Implementation (PLDI ’19). ACM.}

\vspace{.05in}

You, W., Liu, X., Ma, S., \underline{Perry, D.}, Zhang, X., \& Liang, B. (2019,
May). SLF: Fuzzing without Valid Seed Inputs. In
Proceedings of the 41st International Conference on Software Engineering (ICSE '19). ACM.

\vspace{.05in}

{\fontspec[Path = fonts/lato/]{Lato-Bol}\fontsize{10pt}{12pt}\selectfont\bfseries \underline{Perry, D. M.}, Mattavelli, A., Zhang, X., \& Cadar, C. (2017, July). Accelerating array constraints in symbolic execution. In Proceedings of the 26th ACM SIGSOFT International Symposium on Software Testing and Analysis (ISSTA `17). ACM. }
\vspace{.05in}

Huang, J., Aafer, Y., \underline{Perry, D.}, Zhang, X., \& Tian, C. (2017, October). UI driven Android application reduction. In Proceedings of the 32nd IEEE/ACM International Conference on Automated Software Engineering (ASE '17). IEEE Press.

\vspace{.05in}
{\fontspec[Path = fonts/lato/]{Lato-Bol}\fontsize{10pt}{12pt}\selectfont\bfseries Kim, D., Kwon, Y., Liu, P., Kim, I. L., \underline{Perry, D. M.}, Zhang, X., \& Rodriguez-Rivera, G. (2016). Apex: Automatic Programming Assignment Error Explanation (OOPSLA’16). ACM.}

%\runsubsection{Cornell Robot Learning Lab}
%\descript{| Head Undergrad Research}
%\location{Jan 2014 – Present | Ithaca, NY}
%Worked with \textbf{\href{http://www.cs.cornell.edu/~ashesh/}{Ashesh Jain}} and \textbf{\href{http://www.cs.cornell.edu/~asaxena/}{Prof Ashutosh Saxena}} to create \textbf{PlanIt}, a tool which  learns from large scale user preference feedback to plan robot trajectories in human environments.  Publication submitted.
%\sectionsep
%
%\runsubsection{Cornell Phonetics Lab}
%\descript{| Head Undergraduate Researcher}
%\location{Mar 2012 – May 2013 | Ithaca, NY}
%Lead the development of \textbf{QuickTongue}, the first ever breakthrough tongue-controlled game with \textbf{\href{http://conf.ling.cornell.edu/~tilsen/}{Prof Sam Tilsen}} to aid in Linguistics research. Publication submitted.
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section{Awards} 
%\begin{tabular}{rll}
%2014	     & top 52/2500  & KPCB Engineering Fellow\\
%2014	     & 2\textsuperscript{nd} most points  & Google Code Jam, Qualification Round\\
%2014	     & 1\textsuperscript{st}/50  & Microsoft Coding Competition, Cornell\\
%2013	     & National  & Jump Trading Challenge Finalist\\
%2013     & 7\textsuperscript{th}/120 & CS 3410 Cache Race Bot Tournament  \\
%2012     & 2\textsuperscript{nd}/150 & CS 3110 Biannual Intra-Class Bot Tournament \\
%2011     & National & Indian National Mathematics Olympiad (INMO) Finalist \\
%2010     & National & Comp. Soc. of India's National Programming Contest\\
%\end{tabular}
%\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SOCIETIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section{Societies} 
%
%\begin{tabular}{rll}
%2014 	& top 12\%ile    & Tau Beta Pi Engineering Honor Society\\
%2014   & National   & The Global Leadership and Education Forum (tGELF)\\
%2012   &  National  & Golden Key International Honor Society\\
%2012   &  National   & National Society of Collegiate Scholars\\
%\end{tabular}
%\sectionsep

\end{document}
